Assessing Vulnerability to Mental Health Impacts of Weather

### 2020-12-03 doc/temp-sentiment.tex
New text, comments from P. Baylis, additional comments embedded 12/3/20 SESYNC co-working session end.

\section{Introduction}
This work builds on existing work by \citep{baylis_weather_2018}.

@@

@@

Discuss issues with text data (gtp) - that it doesn’t capture emoticons, code switching (e.g., [good job! #fail]), etc.

@@

(sub-section) TEMPERATURE and HUMIDITY
Figure of distribution of max and min temperatures

@@

>>>>

\section{Introduction}
This work builds on existing work by \citep{baylis_weather_2018}. 
Consider going through our paper and using the ABT method for ensuring we are building up a logic string, arguments, why we're doing this, what it answers, etc.

@@

Building on previous findings from Baylis and others, we hypothesize that local ambient weather conditions have a strong connection how people are feeling as expressed in the sentiment of text messages posted on Twitter [H1]. Second, we hypothesize that the weather-sentiment link will be stronger in low-income areas [H2]. Third, we hypothesize that people living in areas with less impervious surfaces and more vegetative tree cover will exhibit higher sentiment scores [H3].

@@

Discuss issues with text data (gtp) - that it doesn’t capture emoticons, code switching (e.g., [good job! \#fail]), etc.

@@

(sub-section) TEMPERATURE and HUMIDITY
Figure of distribution of max and min temperatures
Comment from Patrick Baylis on our "preliminary results". 2nd comment from Patrick

@@

Comment from Patrick Baylis on our "preliminary results" doc
